Improving inference of evolutionary history

### 2014-11-01 slides/osu/slides.tex
Working on osu slides.
Adding photos and cartoons.

        \column{.4\textwidth}

@@

                            \divTimeMapVector = (260,260,260)

@@

                            \divTimeVector = \{260\}

@@

                            \divTimeMapVector = (397,260,260)

@@

                            \divTimeVector = \{260,397\}

@@

                            \divTimeMapVector = (260,397,260)

@@

                            \divTimeVector = \{260,397\}

@@

                            \divTimeMapVector = (260,260,397)

@@

                            \divTimeVector = \{260,397\}

@@

        \begin{onlyenv}<10>

@@

                            \divTimeMapVector = (260,95,397)

@@

                            model = 123

@@

                            \divTimeVector = \{260,95,397\}

@@

        %                     \divTimeMapVector = (260,260,260)

@@

        %                     model = 111

@@

        %                     \divTimeVector = \{260\}

@@

        \begin{onlyenv}<11-13>
                            \divTimeMapVector = (\divTimeMap{1},\ldots,\divTimeMap{\npairs{}})
                            model = \divModel{i}
                            \divTimeVector = \{\divTime{1},\ldots,\divTime{\divTimeNum}\}
        \begin{onlyenv}<14>

@@

                    \item[\geneTreeVector] Gene trees
                    \item[\hkyModelVector] Substitution parameters
                    \item[\demographicParamVector] Demographic parameters

@@

        \begin{uncoverenv}<12->

@@

        \includegraphics<1>[height=6cm]{../images/community-ellipse-small.pdf}
        % \includegraphics<2>[height=6cm]{../images/community-ellipse-barrier-small.pdf}
        \includegraphics<2>[height=6cm]{../images/community-ellipse-split-small.pdf}
        \includegraphics<3>[height=6cm]{../images/div-model-cartoon-taxa.pdf}
        \includegraphics<4>[height=6cm]{../images/div-model-cartoon-shared-no-labels.pdf}
        \includegraphics<5-6>[height=6cm]{../images/div-model-cartoon-shared.pdf}
        \includegraphics<7>[height=6cm]{../images/div-model-cartoon-2-1.pdf}
        \includegraphics<8>[height=6cm]{../images/div-model-cartoon-2-2.pdf}
        \includegraphics<9>[height=6cm]{../images/div-model-cartoon-2-3.pdf}
        \includegraphics<10>[height=6cm]{../images/div-model-cartoon-general.pdf}
        \includegraphics<11-12>[height=6cm]{../images/div-model-cartoon-shared.pdf}
        \includegraphics<13->[height=6cm]{../images/div-model-cartoon-sp-tree-shared.pdf}

@@

\begin{frame}[t]
    \frametitle{Bayesian model choice}
    \begin{block}{\it Full model:}
        \begin{minipage}[c][3.8cm][c]{\linewidth}
            \begin{uncoverenv}<1->
            \[
                p(
                  \divTimeMapVector,
                  \geneTreeVector,
                  \hkyModelVector,
                  \demographicParamVector
                  \given \alignmentVector, \divModel{i})
                  =
                \frac{
                    p(\alignmentVector \given
                      \divTimeMapVector,
                      \geneTreeVector,
                      \hkyModelVector,
                      \demographicParamVector,
                      \divModel{i}
                      )
                      p(
                        \divTimeMapVector,
                        \geneTreeVector,
                        \hkyModelVector,
                        \demographicParamVector
                        \given \divModel{i}
                        )
                    }{p(\alignmentVector \given \divModel{i})}
            \]\vspace{-1mm}
            \end{uncoverenv}
            \begin{uncoverenv}<2->
            \[
                p(\alignmentVector \given \divModel{i}) =
                \int_{\allParameters{i}}
                p(\alignmentVector \given \allParameters{i}, \divModel{i})
                p(\allParameters{i} \given \divModel{i})
                d\allParameters{i}
            \]\vspace{-1mm}
            \end{uncoverenv}
            \begin{uncoverenv}<3->
            \[
                p(\divModel{i} \given \alignmentVector) =
                \frac{
                    p(\alignmentVector \given \divModel{i})
                    p(\divModel{i})
                }{
                    \sum_{i} p(\alignmentVector \given \divModel{i})
                    p(\divModel{i})
                }
            \]\vspace{-1mm}
            \end{uncoverenv}
        \end{minipage}
    \end{block}
    \vspace{1mm}
    \begin{uncoverenv}<4>
        \begin{center}
            \msb: Approximate Bayesian computation (ABC)

@@

\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \begin{table}%[htbp]
            \scriptsize
            \addtolength{\tabcolsep}{-0.09cm}
            \centering
            \begin{tabular}{ l c c }
                % \toprule
                \textbf{Species} & {\boldmath $n_1$} & {\boldmath $n_2$} \\
                \hline
                \textbf{\textsc{Mammals}} & & \\
                \emph{Crocidura beatus}             & 12 & 11 \\
                \emph{Crocidura negrina-panayensis} & 12 & 6  \\
                \emph{Hipposideros obscurus}        & 19 & 9  \\
                \emph{Hipposideros pygmaeus}        & 3  & 12 \\
                \emph{Cynopterus brachyotis}        & 20 & 8  \\
                \emph{Cynopterus brachyotis}        & 8  & 14 \\
                \emph{Haplonycteris fischeri}       & 29 & 8  \\
                \emph{Haplonycteris fischeri}       & 9  & 21 \\
                \emph{Macroglossus minimus}         & 19 & 4  \\
                \emph{Macroglossus minimus}         & 8  & 10 \\
                \emph{Ptenochirus jagori}           & 4  & 7  \\
                \emph{Ptenochirus jagori}           & 8  & 8  \\
                \emph{Ptenochirus minor}            & 30 & 9  \\
                \textbf{\textsc{Squamates}} & & \\
                \emph{Cyrtodactylus gubaot-sumuroi} & 29 & 6  \\
                \emph{Cyrtodactylus annulatus}      & 14 & 3  \\
                \emph{Cyrtodactylus philippinicus}  & 6  & 14 \\
                \emph{Gekko mindorensis}            & 8  & 11 \\
                \emph{Insulasaurus arborens}        & 22 & 10 \\
                \emph{Pinoyscincus jagori}          & 8  & 8  \\
                \emph{Dendrelaphis marenae}         & 6  & 6  \\
                \textbf{\textsc{Anurans}}  & & \\
                \emph{Limnonectes leytensis}        & 4  & 2  \\
                \emph{Limnonectes magnus}           & 2  & 3  \\
                \hline
            \end{tabular}
        \end{table}
    \column{.5\textwidth}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
\end{columns}
\end{frame}

\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \begin{table}%[htbp]
            \scriptsize
            \addtolength{\tabcolsep}{-0.09cm}
            \def\firstrowcolor{}
            \def\secondrowcolor{}
            \def\thirdrowcolor{}
            \def\fourthrowcolor{}
            \def\fifthrowcolor{}
            \only<2>{\def\firstrowcolor{\rowcolor{rowred}}}
            \only<3>{\def\secondrowcolor{\rowcolor{rowred}}}
            \only<4>{\def\thirdrowcolor{\rowcolor{rowred}}}
            \only<5>{\def\fourthrowcolor{\rowcolor{rowred}}}
            \only<6>{\def\fifthrowcolor{\rowcolor{rowred}}}
            \centering
            \begin{tabular}{ l c c }
                % \toprule
                \textbf{Species} & {\boldmath $n_1$} & {\boldmath $n_2$} \\
                \hline
                \textbf{\textsc{Mammals}} & & \\
                \fifthrowcolor  \emph{Crocidura beatus}             & 12 & 11 \\
                \firstrowcolor  \emph{Crocidura negrina-panayensis} & 12 & 6  \\
                \thirdrowcolor  \emph{Hipposideros obscurus}        & 19 & 9  \\
                \secondrowcolor \emph{Hipposideros pygmaeus}        & 3  & 12 \\
                \thirdrowcolor  \emph{Cynopterus brachyotis}        & 20 & 8  \\
                \firstrowcolor  \emph{Cynopterus brachyotis}        & 8  & 14 \\
                \thirdrowcolor  \emph{Haplonycteris fischeri}       & 29 & 8  \\
                \firstrowcolor  \emph{Haplonycteris fischeri}       & 9  & 21 \\
                \thirdrowcolor  \emph{Macroglossus minimus}         & 19 & 4  \\
                \firstrowcolor  \emph{Macroglossus minimus}         & 8  & 10 \\
                \thirdrowcolor  \emph{Ptenochirus jagori}           & 4  & 7  \\
                \firstrowcolor  \emph{Ptenochirus jagori}           & 8  & 8  \\
                \thirdrowcolor  \emph{Ptenochirus minor}            & 30 & 9  \\
                \textbf{\textsc{Squamates}} & & \\
                \fifthrowcolor  \emph{Cyrtodactylus gubaot-sumuroi} & 29 & 6  \\
                \secondrowcolor \emph{Cyrtodactylus annulatus}      & 14 & 3  \\
                \firstrowcolor  \emph{Cyrtodactylus philippinicus}  & 6  & 14 \\
                \firstrowcolor  \emph{Gekko mindorensis}            & 8  & 11 \\
                \firstrowcolor  \emph{Insulasaurus arborens}        & 22 & 10 \\
                \fourthrowcolor \emph{Pinoyscincus jagori}          & 8  & 8  \\
                \firstrowcolor  \emph{Dendrelaphis marenae}         & 6  & 6  \\
                \textbf{\textsc{Anurans}}  & & \\
                \secondrowcolor \emph{Limnonectes leytensis}        & 4  & 2  \\
                \secondrowcolor \emph{Limnonectes magnus}           & 2  & 3  \\
                \hline
            \end{tabular}
        \end{table}
    \column{.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \includegraphics<2>[width=\textwidth]{../images/maps/Philippines-negros_panay.png}
        \includegraphics<3>[width=\textwidth]{../images/maps/Philippines-bohol_mindanao.png}
        \includegraphics<4>[width=\textwidth]{../images/maps/Philippines-leyte_mindanao.png}
        \includegraphics<5>[width=\textwidth]{../images/maps/Philippines-mindanao_samar.png}
        \includegraphics<6>[width=\textwidth]{../images/maps/Philippines-leyte_samar.png}
\end{columns}
\end{frame}

>>>>

        \column{.5\textwidth}

@@

                            \divTimeVector = \{130\}

@@

                            \divTimeMapVector = (130,130,130)

@@

                            \divTimeVector = \{130,397\}

@@

                            \divTimeMapVector = (397,130,130)

@@

                            \divTimeVector = \{130,397\}

@@

                            \divTimeMapVector = (130,397,130)

@@

                            \divTimeVector = \{130,397\}

@@

                            \divTimeVector = \{130,397\}

@@

        \begin{onlyenv}<10-12>

@@

                            \divTimeVector = \{130,397,260\}

@@

                            model = 312

@@

                            \divTimeMapVector = (260,130,397)

@@

        %                     \divTimeVector = \{\divTime{1},\ldots,\divTime{\divTimeNum}\}

@@

        %                     model = \divModel{i}

@@

        %                     \divTimeMapVector = (\divTimeMap{1},\ldots,\divTimeMap{\npairs{}})

@@

        \begin{onlyenv}<13>

@@

                    \item[\allParameters{}] Gene trees
                    \item[\ ] Substitution parameters
                    \item[\ ] Demographic parameters

@@

        \begin{uncoverenv}<11->

@@

        \includegraphics<1>[height=6cm]{../images/dmc-cartoon-islands.pdf}
        \includegraphics<2>[height=6cm]{../images/dmc-cartoon-taxa.pdf}
        \includegraphics<3>[height=6cm]{../images/dmc-cartoon-sea-level.pdf}
        \includegraphics<4>[height=6cm]{../images/dmc-cartoon-shared-no-labels.pdf}
        \includegraphics<5-6>[height=6cm]{../images/dmc-cartoon-shared.pdf}
        \includegraphics<7>[height=6cm]{../images/dmc-cartoon-2-1.pdf}
        \includegraphics<8>[height=6cm]{../images/dmc-cartoon-2-2.pdf}
        \includegraphics<9>[height=6cm]{../images/dmc-cartoon-2-3.pdf}
        \includegraphics<10-11>[height=6cm]{../images/dmc-cartoon-general.pdf}
        \includegraphics<12->[height=6cm]{../images/dmc-cartoon-pop-general.pdf}

@@

\begin{frame}[t]
    \frametitle{Bayesian model choice}
    \begin{block}{\it Full model:}
        \begin{minipage}[c][3.8cm][c]{\linewidth}
            \begin{uncoverenv}<1->
            \[
                p(
                  \divTimeMapVector,
                  \allParameters{}
                  \given \alignmentVector, \divModel{i})
                  =
                \frac{
                    p(\alignmentVector \given
                      \divTimeMapVector,
                      \allParameters{},
                      \divModel{i}
                      )
                      p(
                        \divTimeMapVector,
                        \allParameters{}
                        \given \divModel{i}
                        )
                    }{p(\alignmentVector \given \divModel{i})}
            \]\vspace{-1mm}
            \end{uncoverenv}
            \begin{uncoverenv}<2->
            \[
                p(\alignmentVector \given \divModel{i}) =
                \int_{\divTimeMapVector} \int_{\allParameters{}}
                p(\alignmentVector \given \divTimeMapVector, \allParameters{}, \divModel{i})
                p(\divTimeMapVector, \allParameters{} \given \divModel{i})
                d\divTimeMapVector d\allParameters{}
            \]\vspace{-1mm}
            \end{uncoverenv}
            \begin{uncoverenv}<3->
            \[
                p(\divModel{i} \given \alignmentVector) =
                \frac{
                    p(\alignmentVector \given \divModel{i})
                    p(\divModel{i})
                }{
                    \sum_{i} p(\alignmentVector \given \divModel{i})
                    p(\divModel{i})
                }
            \]\vspace{-1mm}
            \end{uncoverenv}
        \end{minipage}
    \end{block}
    \vspace{1mm}
    \begin{uncoverenv}<4>
        \begin{center}
            \msb: Approximate Bayesian computation (ABC)

@@

\ignore{
\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \begin{table}%[htbp]
            \scriptsize
            \addtolength{\tabcolsep}{-0.09cm}
            \centering
            \begin{tabular}{ l c c }
                % \toprule
                \textbf{Species} & {\boldmath $n_1$} & {\boldmath $n_2$} \\
                \hline
                \textbf{\textsc{Mammals}} & & \\
                \emph{Crocidura beatus}             & 12 & 11 \\
                \emph{Crocidura negrina-panayensis} & 12 & 6  \\
                \emph{Hipposideros obscurus}        & 19 & 9  \\
                \emph{Hipposideros pygmaeus}        & 3  & 12 \\
                \emph{Cynopterus brachyotis}        & 20 & 8  \\
                \emph{Cynopterus brachyotis}        & 8  & 14 \\
                \emph{Haplonycteris fischeri}       & 29 & 8  \\
                \emph{Haplonycteris fischeri}       & 9  & 21 \\
                \emph{Macroglossus minimus}         & 19 & 4  \\
                \emph{Macroglossus minimus}         & 8  & 10 \\
                \emph{Ptenochirus jagori}           & 4  & 7  \\
                \emph{Ptenochirus jagori}           & 8  & 8  \\
                \emph{Ptenochirus minor}            & 30 & 9  \\
                \textbf{\textsc{Squamates}} & & \\
                \emph{Cyrtodactylus gubaot-sumuroi} & 29 & 6  \\
                \emph{Cyrtodactylus annulatus}      & 14 & 3  \\
                \emph{Cyrtodactylus philippinicus}  & 6  & 14 \\
                \emph{Gekko mindorensis}            & 8  & 11 \\
                \emph{Insulasaurus arborens}        & 22 & 10 \\
                \emph{Pinoyscincus jagori}          & 8  & 8  \\
                \emph{Dendrelaphis marenae}         & 6  & 6  \\
                \textbf{\textsc{Anurans}}  & & \\
                \emph{Limnonectes leytensis}        & 4  & 2  \\
                \emph{Limnonectes magnus}           & 2  & 3  \\
                \hline
            \end{tabular}
        \end{table}
    \column{.5\textwidth}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
\end{columns}
\end{frame}

\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \begin{table}%[htbp]
            \scriptsize
            \addtolength{\tabcolsep}{-0.09cm}
            \def\firstrowcolor{}
            % \def\secondrowcolor{}
            % \def\thirdrowcolor{}
            % \def\fourthrowcolor{}
            % \def\fifthrowcolor{}
            \only<2>{\def\firstrowcolor{\rowcolor{rowred}}}
            % \only<3>{\def\secondrowcolor{\rowcolor{rowred}}}
            % \only<4>{\def\thirdrowcolor{\rowcolor{rowred}}}
            % \only<5>{\def\fourthrowcolor{\rowcolor{rowred}}}
            % \only<6>{\def\fifthrowcolor{\rowcolor{rowred}}}
            \centering
            \begin{tabular}{ l c c }
                % \toprule
                \textbf{Species} & {\boldmath $n_1$} & {\boldmath $n_2$} \\
                \hline
                \textbf{\textsc{Mammals}} & & \\
                  \emph{Crocidura beatus}             & 12 & 11 \\
                \firstrowcolor  \emph{Crocidura negrina-panayensis} & 12 & 6  \\
                  \emph{Hipposideros obscurus}        & 19 & 9  \\
                  \emph{Hipposideros pygmaeus}        & 3  & 12 \\
                  \emph{Cynopterus brachyotis}        & 20 & 8  \\
                \firstrowcolor  \emph{Cynopterus brachyotis}        & 8  & 14 \\
                  \emph{Haplonycteris fischeri}       & 29 & 8  \\
                \firstrowcolor  \emph{Haplonycteris fischeri}       & 9  & 21 \\
                  \emph{Macroglossus minimus}         & 19 & 4  \\
                \firstrowcolor  \emph{Macroglossus minimus}         & 8  & 10 \\
                  \emph{Ptenochirus jagori}           & 4  & 7  \\
                \firstrowcolor  \emph{Ptenochirus jagori}           & 8  & 8  \\
                  \emph{Ptenochirus minor}            & 30 & 9  \\
                \textbf{\textsc{Squamates}} & & \\
                  \emph{Cyrtodactylus gubaot-sumuroi} & 29 & 6  \\
                  \emph{Cyrtodactylus annulatus}      & 14 & 3  \\
                \firstrowcolor  \emph{Cyrtodactylus philippinicus}  & 6  & 14 \\
                \firstrowcolor  \emph{Gekko mindorensis}            & 8  & 11 \\
                \firstrowcolor  \emph{Insulasaurus arborens}        & 22 & 10 \\
                  \emph{Pinoyscincus jagori}          & 8  & 8  \\
                \firstrowcolor  \emph{Dendrelaphis marenae}         & 6  & 6  \\
                \textbf{\textsc{Anurans}}  & & \\
                  \emph{Limnonectes leytensis}        & 4  & 2  \\
                  \emph{Limnonectes magnus}           & 2  & 3  \\
                \hline
            \end{tabular}
        \end{table}
    \column{.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \includegraphics<2>[width=\textwidth]{../images/maps/Philippines-negros_panay.png}
        % \includegraphics<3>[width=\textwidth]{../images/maps/Philippines-bohol_mindanao.png}
        % \includegraphics<4>[width=\textwidth]{../images/maps/Philippines-leyte_mindanao.png}
        % \includegraphics<5>[width=\textwidth]{../images/maps/Philippines-mindanao_samar.png}
        % \includegraphics<6>[width=\textwidth]{../images/maps/Philippines-leyte_samar.png}
\end{columns}
\end{frame}
}

\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/cyrt-agusanensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
    \column{.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \includegraphics<2>[width=\textwidth]{../images/maps/Philippines-negros_panay.png}
\end{columns}
\end{frame}
